Supplementary Materials for \"COATi: statistical pairwise alignment of protein coding sequences\

### 2024-01-28 alignpair_letter.tex
Add more results and figures

\usepackage{tikz}
\usetikzlibrary{arrows,automata,positioning,shapes,decorations.text,backgrounds,matrix}
\usepackage{wrapfig, framed}
\usepackage[font=small,labelfont=bf]{caption}
\usepackage[hidelinks]{hyperref}
\usepackage{listings}
\usepackage{relsize}
\usepackage[left]{lineno}
\usepackage{colortbl}
\usepackage{multicol}

@@

Humans and gorillas are two closely related species with very different levels of genome curation. The human reference genome has been revised dozens of times and is currently on version GRCh38.p14, while the gorilla reference genome has only been revised a handful of times and is currently on version gorGor4 \citep[cf.\ ENSEMBL database v110;][]{ensembl_hubbard_2002}. Additionally significant levels of investment have been made to correctly identify and annotate human genes, while gorilla annotations have received limited support in comparison. Together, these reference genomes provide a good opportunity to compare COATi against other aligner as they offer one genome that is high-quality (human) and sister genome that is lower-quality (gorilla).

@@

We aligned our dataset of human-gorilla orthologs using all six alignment methods and calculated multiple biological and technical statistics on each alignment in order to compare how different alignment methods influence biological conclusions.
%
Additionally, we checked alignments to ensure that our pipeline did not introduce any artifacts into the results, including unexpected characters, empty columns, and aligned sequences of different lengths. We also generated checksums of our sequences to ensure that they were not modified during alignment.

@@

Alignment inference impacts the estimation of evolutionary distances. To quantify the impact of aligners on the estimation of evolutionary distances, we calculated Kimura's 2-parameter distance \citep[K2P;][]{kimura1980simple} for each sequence-pair and aligner combination. K2P corrects for multiple mutations at a site and takes into account differences in transition and transversion rates. It also assumes equal nucleotide frequencies and no variations in the rate of substitution across sites. While Kimura's 2-parameter distance is more suitable for non-coding sequences, it is straight forward to calculate and provides a quantitative measure of the evolutionary divergence between sequences. We used the R software package ape \citep{paradis2019ape} to calculate K2P distances.
%
Since aligners influence evolutionary distances based on their tendencies to insert gaps into sequences, we also quantified the lengths and phases of gaps introduced by each method as well as the fraction of nucleotides that are aligned against a gap.

@@

\subsection*{Empirical Simulation Algorithm}

% 8263 gapless genes.
% 5864 gapped genes.

In order to compare COATi against other aligners on realistic datasets with known alignments, we developed a procedure to introduce realistic gap patterns into human-gorilla orthologous gene pairs that did not previous contain indels. Briefly, we downloaded 16000 human genes and their gorilla orthologs from the ENSEMBL database \citep{ensembl_hubbard_2002}. After downloading, we removed 2232 sequence-pairs longer than 6000 nucleotides and aligned the remaining pairs with the five alignment methods. Next we separated sequence pairs into two sets: (1) 6048 sequence pairs for which at least one aligner added gaps and (2) 7761 sequence pairs for which all five aligners did not introduce any gaps. We identified gap patterns from the sequence pairs that were aligned with gaps and randomly introduced them into the ungapped sequence pairs. We used an equal number of randomly sampled gap patterns from each aligner to produce a benchmark set of known alignments. The phases of gaps were preserved as were the spacings of any clusters of gaps. Segments of matches that were 99 nucleotides or longer were allowed to change length to accommodate the length of the ungapped sequence pair. (This criteria was recursively lowered if gap pattern did not fit the ungapped sequence pair.)

For example, consider the gapped alignment represented by the CIGAR string
%
``170M 3D 10M 6I 102M'' % Can use \allowbreak{} here instead of space
%
applied to an ungapped alignment of human and gorilla sequences that are 300 nucleotides long. First, we modify the CIGAR string to insert flexible lengths for any match segment that is 99 or more nucleotides long while preserving phase. This results in a new CIGAR string of
%
``101M *M 3D 10M 6I 99M *M'',
%
where * represents the locations that have flexible length. Considering only matches and deletions, this CIGAR string has 213 fixed nucleotides, leaving 87 nucleotides in the human sequence to be allocated to the flexible locations. Since there are two locations of flexible length, we draw one random break point uniformly while maintaining phase, producing the final CIGAR string of
%
``101M 9M 3D 10M 6I 99M 78M'',
%
which is used to add gaps into the target, ungapped sequence pair.
To apply deletions, we remove the corresponding nucleotides from the gorilla sequence, and to apply insertions, we add random nucleotides according to their stationary frequency to the gorilla sequence at the corresponding locations. The human sequence is left unchanged.

@@

\subsection*{Alignment Accuracy Measures}

We used multiple statistics to to quantify the similarity between each alignment in the benchmark and the corresponding output obtained by the different tools.

Alignment error also negatively impacts the estimation of evolutionary distances and phylogenetic trees. To quantify the impact of aligners on the estimation of evolutionary distances, we compared Kimura's 2-parameter distance \citep[K2P;][]{kimura1980simple} calculated for the estimated and benchmark alignments.

Alignment error negatively impacts the identification of genes that have experienced positive and negative selection.

Alignment error negatively impacts the identification of genes that have experienced positive and negative selection. To evaluate the impact of aligners on selection identification, we estimated $K_S$ and $K_A$ statistics (also known as $d_s$ and $d_n$) for each estimated alignment and compared them to the benchmark alignment.

\paragraph{Alignment Error.}
To quantify the error between estimated alignments and the benchmark alignments, we used the alignment error metric $d_{seq}$ \citep{metrics_blackburne_whelan_2011}. Intuitively, $d_{seq}$ ranges between zero and one and can be interpreted as the fraction of nucleotides in the sequence pair that are aligned differently between estimated and benchmark alignments. This metric summarizes each alignment by building homology sets for each nucleotide in the sequence pair. Briefly, if an alignment column contains position $i$ from the first sequence and position $j$ from the second sequence, then $\{j\}$ is the homology set for position $i$ in the first sequence and $\{i\}$ is the homology set for position $j$ in the second sequence. If a position is aligned against a gap, then its homology set is simply $\{\text{gap}\}$. This treats all gaps equally as the location of the gap is not recorded. Finally, $d_{seq}$ is calculated  between an estimated and a benchmark alignment as the average, normalized Hamming distance between the homology sets for each nucleotide in the sequence pair. See \cite{metrics_blackburne_whelan_2011} for further details.

@@

\paragraph{Perfect, Imperfect, and Best Alignments.}
We quantified the number of perfect, imperfect and best alignments each aligner produced. We define perfect alignments as alignments with a distance of zero to their benchmark alignment ($d_{seq} = 0$) or any alignment that is evolutionary equivalent to an alignment with a distance of zero. Equivalency was included in our definition of perfect alignments to prevent the manner by which aligners break ties between multiple optimal alignments from impacting our results. Evolutionary equivalence was determined by scoring alignments using COATi's marginal model. Any alignment that had a score which matched the score of its benchmark alignment was considered perfect even if its distance to the benchmark was greater than zero.
%
Imperfect alignments are defined as alignments that are not perfect when another method successfully produces a perfect alignment for the same pair of sequences.
%
Best alignments are the alignments that the lowest distance $d_{seq}$ to the true alignment, including ties.
%
Taken together, these three statistics not only allow a direct comparison of aligners but also expose instances where all aligners fall short of achieving a perfect result.

@@

COATi was not able to align 23 sequence pairs, PRANK was not able to align 24 sequence pairs, and COATi-rev was not able to align 193 sequence pairs. MAFFT, MACSE, and ClustalΩ were able to align all sequence pairs, although the latter received some help from our wrapper script.

\begin{figure}[h!]
    \centering%
    \includegraphics{figures/fig-k2p-empirical.pdf}
    \par
    \caption{COATi's alignments produce biologically reasonable evolutionary distances. (a) The distribution of K2P distances inferred from alignments generated by each method. The averages of each distribution are indicated by vertical lines. The averages are COATi = 0.0084, ClustalΩ = 0.0178, MACSE = 0.0149, MAFFT = 0.0154, PRANK = 0.0092, and COATi-rev = 0.0084. (b) The distribution of the differences between distances inferred by COATi and other methods. The X-axes of both plots have been pseudo-log transformed using the inverse hyperbolic sine.}
    \label{fig:k2p-empirical}
\end{figure}

@@

@@

% Software comparison table
\begin{table}[!ht]
\centering
\input{figures/table-comp}
 \vspace{1mm}
 \footnotesize{\textsuperscript{*}PRANK produced 42 empty alignments, calculations are based on 7719 alignments.}
 \caption{COATi generates better alignments than other alignment algorithms. Results of COATi, PRANK, MAFFT, Clustal$\Omega$, and MACSE aligning 7761 empirically simulated sequence pairs. Best alignments have the lowest $d_{seq}$ (including ties), perfect alignments have the same score as the true alignment, and imperfect alignments have a different score than the true alignment when at least one method found a perfect alignment.}
 \label{table:comp}
\end{table}

@@

\section*{Availability}
The source code for COATi, along with documentation, is freely available on GitHub: \url{https://github.com/CartwrightLab/coati} and is implemented in C++. Additional information, code, and workflows to replicate the analysis can be found on GitHub: \url{https://github.com/jgarciamesa/coati-testing}.

>>>>

\usepackage{tikz}
\usetikzlibrary{arrows,automata,positioning,shapes,decorations.text,backgrounds,matrix}
\usepackage{wrapfig, framed}
\usepackage[font=small,labelfont=bf]{caption}
\usepackage[hidelinks]{hyperref}
\usepackage{listings}
\usepackage{relsize}
\usepackage[left]{lineno}
\usepackage{colortbl}
\usepackage{multicol}
\usepackage{booktabs}

@@

Humans and gorillas are two closely related species with very different levels of genome curation. The human reference genome has been revised dozens of times and is currently on version GRCh38.p14, while the gorilla reference genome has only been revised a handful of times and is currently on version gorGor4 \citep[cf.\ ENSEMBL database v110;][]{ensembl_hubbard_2002}. Additionally significant levels of investment have been made to correctly identify and annotate human genes, while gorilla annotations have received limited support in comparison. Together, these reference genomes provide a good opportunity to compare COATi against other aligners as they offer one genome that is high-quality (human) and sister genome that is lower-quality (gorilla).

@@

We aligned our dataset of human-gorilla orthologs using all six alignment methods and calculated multiple biological and technical statistics on each alignment in order to compare how different alignment methods influence biological conclusions.
%
Additionally, we checked alignments to ensure that our pipeline did not introduce any artifacts into the results, including unexpected characters, empty columns, and aligned sequences of different lengths. We also generated checksums of our sequences with gaps removed to ensure that they were not modified during alignment.

@@

Alignment inference impacts the estimation of evolutionary distances. To quantify the impact of aligners on the estimation of evolutionary distances, we calculated Kimura's 2-parameter distance \citep[K2P;][]{kimura1980simple} for each sequence-pair and aligner combination. K2P corrects for multiple mutations at a site and takes into account differences in transition and transversion rates. It also assumes equal nucleotide frequencies and no variation in the rate of substitution across sites. While Kimura's 2-parameter distance is more suitable for non-coding sequences, it is straight forward to calculate and provides a quantitative measure of the evolutionary divergence between sequences. We used the R software package ape \citep{paradis2019ape} to calculate K2P distances.
%
Since aligners influence evolutionary distances based on their tendencies to insert gaps into sequences, we also quantified the phases and lengths of gaps introduced by each method as well as the fraction of nucleotides that are aligned against a match, mismatch, or gap.

@@

\subsection*{Simulated Benchmark Alignments}

In order to compare COATi against other aligners on realistic datasets with known alignments, we developed a procedure to introduce realistic gap patterns into human-gorilla orthologous gene pairs that did not previous contain indels. We separated our 14,127 empirical sequence pairs into two sets: %
(1) 8261 sequence pairs that did not contain any gaps when aligned by COATi FST, ClustalΩ, MACSE, MAFFT, and PRANK, and (2) 5821 sequence pairs for which at least one of these five aligners added gaps.
(45 pairs that could not be aligned by at least one aligner were dropped.) We identified gap patterns from the sequence pairs that were aligned with gaps and randomly introduced them into the ungapped sequence pairs. We used an equal number of randomly sampled gap patterns from each aligner to produce a benchmark set of known alignments. The phases of gaps were preserved as were the spacings of any clusters of gaps. Segments of matches that were 96 nucleotides or longer were allowed to change length to accommodate the length of the ungapped sequence pair. (This criteria was recursively lowered if gap pattern did not fit the ungapped sequence pair.)

For example, consider the gapped alignment represented by the CIGAR string
%
``170M 3D 10M 6I 102M'' % Can use \allowbreak{} here instead of space
%
applied to an ungapped alignment of human and gorilla sequences that are 300 nucleotides long. First, we modified the CIGAR string to insert flexible lengths for any match segment that is 96 or more nucleotides long while preserving phase. This results in a new CIGAR string of
%
``98M *M 3D 10M 6I 96M *M'',
%
where * represents the locations that have flexible length. Considering only matches and deletions, this CIGAR string has 207 fixed nucleotides, leaving 93 nucleotides in the human sequence to be allocated to the flexible locations. Since there are two locations of flexible length, we drew one random break point uniformly while maintaining phase, producing the final CIGAR string of
%
``98M 12M 3D 10M 6I 96M 81M'',
%
which was used to add gaps into the target, ungapped sequence pair.
To apply deletions, we removed the corresponding nucleotides from the gorilla sequence, and to apply insertions, we added nucleotides to the gorilla sequence by sampling codons from their stationary frequency while respecting gap phases. The human sequence was left unchanged.
%
We generated a benchmark of 8261 sequence pairs with known alignments using this strategy.

@@

\subsection*{Measuring Aligner Accuracy}

We aligned our benchmark alignments using our suite of aligners and quantified the similarity of each alignment that was produced to its respective benchmark. As above, we measured Kimura's 2-parameter distance \citep{kimura1980simple} and $K_A/K_S$ \citep{ka_ks_li_1993} for the benchmark and estimated alignments. Additionally, we quantified the error of estimated alignments using the $d_{seq}$ metric \citep{metrics_blackburne_whelan_2011}.

Intuitively, $d_{seq}$ ranges between zero and one and can be interpreted as the fraction of nucleotides in the sequence pair that are aligned differently between estimated and benchmark alignments. This metric summarizes each alignment by building homology sets for each nucleotide in the sequence pair. Briefly, if an alignment column contains position $i$ from the first sequence and position $j$ from the second sequence, then $\{j\}$ is the homology set for position $i$ in the first sequence and $\{i\}$ is the homology set for position $j$ in the second sequence. If a position is aligned against a gap, then its homology set is simply $\{\text{gap}\}$. This treats all gaps equally as the location of the gap is not recorded. Finally, $d_{seq}$ is calculated  between an estimated and a benchmark alignment as the average, normalized Hamming distance between the homology sets for each nucleotide in the sequence pair. See \cite{metrics_blackburne_whelan_2011} for further details.

@@

Using $d_{seq}$ we quantified the number of perfect, imperfect and best alignments each aligner produced. We define perfect alignments as alignments with a distance of zero to their benchmark alignment ($d_{seq} = 0$) or any alignment that is evolutionary equivalent to an alignment with a distance of zero. Equivalency was included in our definition of perfect alignments to prevent the manner by which aligners break ties between multiple optimal alignments from influencing our results. Evolutionary equivalence was determined by scoring alignments using COATi's marginal model. Any alignment that had a score which matched the score of its benchmark alignment was considered perfect even if its distance to the benchmark was greater than zero.
%
Imperfect alignments are defined as alignments that are not perfect when another method successfully produces a perfect alignment for the same pair of sequences.
%
Best alignments are the alignments that the lowest distance $d_{seq}$ to the true alignment, including ties.
%
Taken together, these three statistics not only allow a direct comparison of aligners but also expose instances where all aligners fall short of achieving a perfect result.

@@

As expected, COATi was not able to align 23 sequence pairs and COATi-rev was not able to align 193 sequence pairs. PRANK was not able to align 24 sequence pairs. MAFFT, MACSE, and ClustalΩ were able to align all sequence pairs, although the latter received some help from its wrapper script. Additionally, MAFFT produced alignments with columns that contained only gaps, which were removed by its wrapper script.
A total of 10296 sequence pairs were aligned equivalently by all five methods, including 8261 sequence pairs that did not contain any gaps, 664 that had identical alignments, and another 1371 that had identical scores.

Compared to other aligners, COATi inferred more indels and aligned more nucleotides against a gap while producing fewer mismatches (Tab.~\ref{tab:gaps-empirical}). Additionally, COATi inferred that 60\% indels occurred in phase 1 or phase 2 in our coding sequences. MACSE's amino-acid aware nucleotide model inferred 7\%, while MAFFT's non-coding DNA model inferred 48\%. PRANK's codon and ClustalΩ's amino-acid models were constrained by their assumptions and inferred no phase 1 or phase 2 gaps. Note that ClustalΩ's gaps with phases of 1 and 2 were created by our wrapper script handling DNA sequences with lengths that are not multiples of 3.

\begin{table}[h]
\caption{\label{tab:gaps-empirical}COATi produced more indels and fewer mismatches compared to other aligners.}
\centering
\begin{tabular}[t]{lrrrccc}
\toprule
\multicolumn{1}{c}{ } & \multicolumn{3}{c}{Indel Phases\textsuperscript{1}} & \multicolumn{3}{c}{Homology Patterns\textsuperscript{2}}\\
\cmidrule(l{3pt}r{3pt}){2-4}
\cmidrule(l{3pt}r{3pt}){5-7}
Method & \multicolumn{1}{c}{1} & \multicolumn{1}{c}{2} & \multicolumn{1}{c}{3} & Matches & Mismatches & Gaps\\
\midrule
COATi & 4493 & 3962 & 5822 & 95.93\% & 0.79\% & 3.28\%\\
\addlinespace
ClustalΩ & 8 & 6 & 10230 & 95.93\% & 1.54\% & 2.52\%\\
\addlinespace
MACSE & 455 & 497 & 13017 & 96.13\% & 1.33\% & 2.54\%\\
\addlinespace
MAFFT & 2317 & 2631 & 5458 & 96.12\% & 1.36\% & 2.52\%\\
\addlinespace
PRANK & 0 & 0 & 10862 & 95.64\% & 0.84\% & 3.52\%\\
\addlinespace
COATi-rev & 3992 & 3775 & 6176 & 95.95\% & 0.79\% & 3.25\%\\
\bottomrule
\addlinespace
\multicolumn{7}{p{30em}}{\footnotesize\textsuperscript{1}Total number of indels inferred by each aligner separated by phase.}\\
\multicolumn{7}{p{30em}}{\footnotesize\textsuperscript{2}The percent of nucleotides that were aligned against a match, mismatch, and gap respectively. This is different than the percent of columns that contain a match, mismatch, or gap because match and mismatch columns are counted twice.}

\end{tabular}

% The homology pattern columns contain the percent of nucleotides that were aligned
% against a match, mismatch, and gap respectively. Note that this is different than the percent of columns that
% contain a match, mismatch, or gap because match and mismatch columns are counted twice.
\end{table}

\paragraph{Evolutionary Distances.}

The distribution of evolutionary distances for COATi, COATi-rev, and PRANK were biologically reasonable  for human-gorilla gene pairs, with means 0.8\%--0.9\% (Fig.~\ref{fig:k2p-empirical}a). Conversely, the means for ClustalΩ, MACSE, and MAFFT were much higher, 1.5\%--1.8\%. These larger means are due to the fact that the right tails of the distributions for ClustalΩ, MACSE, and MAFFT were larger than the other methods. The differences between the distances inferred by COATi and other methods also shows ClustalΩ, MACSE, and MAFFT producing higher distance estimates for a subset of sequences (Fig.~\ref{fig:k2p-empirical}b).
%
COATi's alignments produced significantly lower K2P distances than ClustalΩ, MACSE, MAFFT, and PRANK. Single-tailed Wilcoxon signed-rank tests on matched data produced p-values $< 2.2\times10^{-16}$. Additionally, COATi's K2P distances did not depend on whether human or gorilla was used as the reference sequence (p-value of $0.4212$ for a two-sided test). Additional analysis of the empirical alignments can be found in Supplementary Methods.

@@

\begin{figure}[h!]
    \centering%
    \includegraphics{figures/fig-k2p-empirical.pdf}
    \par
    \caption{COATi's alignments produce biologically reasonable evolutionary distances. (a) The distribution of K2P distances inferred from alignments generated by each method. The averages of each distribution are indicated by vertical lines. The averages are COATi = 0.0084, ClustalΩ = 0.0178, MACSE = 0.0149, MAFFT = 0.0154, PRANK = 0.0092, and COATi-rev = 0.0084. (b) The distribution of the differences between distances inferred by COATi and other methods. The X-axes of both plots have been pseudo-log transformed using the inverse hyperbolic sine.\label{fig:k2p-empirical}}
\end{figure}

\paragraph{Selection.}

The vast majority of sequence pairs (12,344) were identified as showing evidence of negative selection when they were aligned using COATi, ClustalΩ, MACSE, MAFFT, PRANK, and COATi-rev (Fig.~\ref{fig:sel-empirical}). Another 1087 sequence pairs were identified as showing evidence of positive selection when they were aligned using all 6 strategies. The most common pattern that showed disagreement between aligners were 91 sequence pairs that were identified as positively selected by COATi, PRANK, and COATi-rev. The most common singleton pattern was 64 sequence pairs identified as positively selected only by MAFFT. Notably, 36 sequence pairs were identified as positively selected and 9 sequence pairs were identified as negatively selected by by COATi and COATi-rev only.
%
In total, COATi identified 1,367 (\sim{}10\%) sequence pairs as showing evidence of positive selection. ClustalΩ identified 1,228. MACSE identified 1,183. MAFFT identified 1,340. And PRANK identified 1,349.

\begin{figure}[h!]
    \centering%
    \includegraphics{figures/fig-sel-empirical.pdf}
    \par
    \caption{Aligners varied in which sequence pairs they identified as undergoing positive selection.
    In this UpSet plot, the bottom panel displays the 16 most frequent intersection patterns among aligners. A black circle represents positive selection. The most frequent pattern was that no aligner found positive selection while the second most frequent pattern was that all aligners found positive selection. Other patterns involved a disagreement between aligners about whether a sequence pair showed evidence of positive or negative selection. The top panel displays the number of sequence pairs in each grouping.
%
    \label{fig:sel-empirical}}
\end{figure}

\subsection*{Benchmark Results}

% Software comparison table
\begin{table}[!ht]
\definecolor{bestcolor}{RGB}{230,230,230}%
\centering
\caption{COATi generates better alignments than other alignment algorithms on semi-empirical benchmarks.\label{table:comp}}
%
% Copied from tables/benchmarks.tex
% footnotes and \addlinespace are manually added
\begin{tabular}{rccccc}
  \toprule
 & COATi & ClustalΩ & MACSE & MAFFT & PRANK \\ 
  \midrule
Average Alignment Error ($d_{seq}$) & \cellcolor{bestcolor}0.23\% & 2.65\% & 1.37\% & 1.67\% & 1.02\% \\
\addlinespace 
  Number of Best\textsuperscript{1} Alignments & \cellcolor{bestcolor}7050 & 3988 & 5226 & 5918 & 6128 \\ 
  Number of Perfect\textsuperscript{2} Alignments & \cellcolor{bestcolor}6795 & 3954 & 5138 & 5840 & 5860 \\ 
  Number of Imperfect\textsuperscript{3} Alignments & \cellcolor{bestcolor} 850 & 3691 & 2507 & 1805 & 1785 \\
  \addlinespace 
  RMSE for K2P Distances & \cellcolor{bestcolor}0.000694 & 0.0920 & 0.0528 & 0.0561 & 0.0305 \\ 
  Overestimated K2P Distances & \cellcolor{bestcolor}10.3\% & 52.7\% & 38.0\% & 26.2\% & 25.6\% \\ 
  \addlinespace
  F\textsubscript{1} for Negative Selection & \cellcolor{bestcolor}99.8\% & 97.6\% & 98.4\% & 98.3\% & 99.1\% \\ 
  F\textsubscript{1} for Positive Selection & \cellcolor{bestcolor}97.8\% & 77.2\% & 84.9\% & 85.5\% & 91.8\% \\ 
   \bottomrule
   \addlinespace
\multicolumn{6}{p{40em}}{\textsuperscript{1}Best alignments have the lowest $d_{seq}$ (including equivalent alignments)}\\
\multicolumn{6}{p{40em}}{\textsuperscript{2}Perfect alignments have $d_{seq} = 0$ (including equivalent alignments)}\\
\multicolumn{6}{p{40em}}{\textsuperscript{3}Imperfect alignments are alignments that are not perfect when at least one method found a perfect alignment.}\\
\end{tabular}
\end{table}

\clearpage

@@

@@

\section*{Availability}
The source code for COATi, along with documentation, is freely available on GitHub: \url{https://github.com/CartwrightLab/coati} and is implemented in C++. COATi is released under an MIT license. Additional information, code, and workflows to replicate the analysis can be found on GitHub: \url{https://github.com/jgarciamesa/coati-testing} and \url{https://github.com/jgarciamesa/alignpair_letter}.
